On the number of tiles \touched{} by a\\ line segment on a rectangular grid

### 2021-08-19 paper.tex
Ranges of length in the square case
This will be used for the probability of maximum

>>>>

From Theorem~\ref{theo: funt, sq, form} it is easily seen that odd values of $\funt(\len)$ correspond to $\isoli = \jsoli$, whereas even values are achieved with $\jsoli = \isoli+1$. Given $\tiles \geq 3$ with $t$ odd, $\funt(\len) = \tiles$ if and only if $\len \in ((\tiles-3)/\sqrt{2}, \sqrt{(\tiles^2-4\tiles+5)/2}]$. For $t$ even, $\funt(\len) = \tiles$ if and only if $\len \in (\sqrt{(\tiles^2-6\tiles+10)/2}, (\tiles-2)/\sqrt{2}]$.
